%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a single column version of the popular Deedy Resume created by
% Debarghya Das. 
%
% Some extra commands are defined in the .cls file for simplification
%
% Compile with XeLaTex
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{single_column_resume}
\setmainfont[Path = fonts/lato/]{Lato-Reg}
\usepackage{xcolor}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Header
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\namesection{Makena}{Schwinn} { \\
	makenaschwinn@berkeley.edu \\
	415-827-9022 \\
	\url{github.com/makenaschwinn} \\
	\url{linkedin.com/in/makenaschwinn/}
} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\noindent\runsubsection{University of California, Berkeley}
\hfill \location{Aug 2016 – Dec 2020}
\vspace{2pt}
\descript{ Degrees in Computer Science \& Business Administration}
\hfill \location{GPA: 3.8}
\vspace{3pt}
% \award{\textbf{Awards:} Outstanding Teaching Award (2019), Dean’s List (2018, 2019, 2020), Honors to Date (2018)} \\
% \award{\textbf{Honors:} Upsilon Pi Epsilon (Computer Science Honor Society), Accel Scholars (mentorship program led by Accel)}
% \setlength{\parindent}{5ex}
% \runsubsubsection{\textbf{Awards:} Outstanding Teaching Award (2019), Dean’s List (2018, 2019, 2020), Honors to Date (2018)} \\
% \vspace{2pt}
% \runsubsubsection{\textbf{Honors:} Upsilon Pi Epsilon (Computer Science Honor Society), EECS Dept. Accel Scholar} \\
\runsubsubsection{Awards:} \textlist{Dean’s List (2018, 2019, 2020), Outstanding Teaching Award (2018), Honors to Date (2018)}\\
\vspace{2pt}
\runsubsubsection{Honors:} \textlist{Upsilon Pi Epsilon (Computer Science Honor Society), EECS Department Accel Scholar}\\
\vspace{2pt}
% \runsubsubsection{Coursework:}
% \textlist{Machine Learning (CS 189), Optimization (EECS 127), Artificial Intelligence (CS 188), User Interface Design (CS 160), Data Science (DATA 8, 100), Data Structures (CS 61B), Linear Algebra \& Differential Equations (MATH 54),  Discrete Math \& Probability (EECS 70), Multivariable Calculus (MATH 53), Physics (7A), Finance (UGBA 103), Micro \& Macro Economics (UGBA 101A, B \& ECON 2, 134), Strategy in IT (UGBA 190), Intellectual Property for Entrepreneurship (UGBA 190T), Marketing (UGBA 106)}\\
\runsubsubsection{Computer Science Courses:} 
\textlist{Machine Learning (CS 189), Artificial Intelligence (CS 188), Data Science (DATA 8, 100), Data Structures \& Algorithms (CS 61B), User Interface Design (CS 160)}
\\
\runsubsubsection{Mathematics Courses:} 
\textlist{Optimization (EECS 127), Discrete Math \& Probability (EECS 70), Linear Algebra \& Differential Equations (MATH 54),   Multivariable Calculus (MATH 53), Physics (7A)}
\\
\runsubsubsection{Business Courses:}
\textlist{Finance (UGBA 103), Micro \& Macro Economics (UGBA 101A, B \& ECON 2, 134), Strategy for the IT Firm (UGBA 190), Intellectual Property for Entrepreneurship (UGBA 190T), Marketing (UGBA 106)}
\\

{\setlength{\parindent}{0cm}}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Industry Experience}

\noindent\runsubsection{Deloitte Consulting}
\descript{| Business Technology Analyst Intern}
\hfill \location{ Jun 2019 – Aug 2019}
\begin{tightemize}
    \item Identified growth opportunities for Google Cloud Platform through Deloitte’s Strategy and Analytics team.
    \item Sourced deals for Google’s strategic investment fund and evaluated potential investments for profitability. 
    \item Prepared high-visibility presentations to communicate deal status and sourcing methodology to leadership.
\end{tightemize}
\sectionsep

\noindent\runsubsection{Amazon Lab126}
\descript{| Software Engineering Intern}
\hfill \location{ May 2018 – Aug 2018}
\begin{tightemize}
    \item Designed custom data structures to efficiently process data from 50+ million Amazon consumer devices daily.
    \item Created and integrated scalable survival analysis tool to examine real-time stability and performance metrics.
    \item Utilized results to influence decision making on software releases and target future device improvements.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Research
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Academia}

\noindent\runsubsection{Berkeley Integrated System for Transit Optimization}
\descript{| Researcher}
\hfill \location{ Aug 2019 – present}
\begin{tightemize}
    \item Improved existing optimization algorithm by 40\% by implementing hypervolume expansion as the optimization objective in an open-source, multi-agent transportation simulation framework.
    \item Generated empirical Laffer curve to determine potential optimal toll rates in urban environments.
    \item Supervised by Prof. Alex Bayen, in collaboration with San Francisco County Transportation Authority, with anticipated paper publication in ACM Transactions on Evolutionary Learning and Optimization in late 2020.
\end{tightemize}
\sectionsep

\noindent\runsubsection{UC Berkeley Department of Data Science}
\descript{| Data 8 Teaching Assistant}
\hfill \location{ Jan 2017 – May 2019}
\begin{tightemize}
    \item Taught data science concepts (Python, probability, bootstrapping, confidence intervals, regression, classification) in weekly labs, small group tutoring, and office hours; created exams, programming assignments, and worksheets.
    \item Received Fall 2018 Outstanding Teaching Award, presented to top 5\% of TAs.
\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Technical Projects}
\runsubsection{Credit Card Fraud Classifier}
\descript{(Python, Keras)}
\hfill \location{550 lines}
\begin{tightemize}
   \item Classified transaction data into authentic and fraudulent purchases in collaboration with two other developers, using neural networks, k-menas, and logistic regression.
\end{tightemize}
\sectionsep

\runsubsection{Relational Database Management System}
\descript{(Java, SQL)}
\hfill \location{650 lines}
\begin{tightemize}
   \item Built SQL-like database management system and query language. Developed unit and integration tests.
\end{tightemize}
\sectionsep

\runsubsection{Version-Control System}
\descript{(Java)}
\hfill \location{1,300 lines}
\begin{tightemize}
   \item Designed and implemented offline version-control system, reminiscent of Git, from scratch. Functionality includes: save, branch, merge, and restore versions of files from command line.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Skills
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\runsubsubsection{Programming Languages:}
\textlist{Python (Scikit-learn, Keras, Hyperopt, Pandas, Matplotlib), Java, C, SQL, R, HTML}
\\
\runsubsubsection{Other Tools:}
\textlist{Git, AWS EC2/S3/Redshift, Excel (linear programming, sensitivity analysis, simulation, pivot tables)}
\\
\runsubsubsection{Non-Technical:}
\textlist{Public Speaking, Outstanding Written \& Verbal Communication, Teamwork, Leadership, Spanish}

\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     End
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}